A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-20 paper/elsarticle/elsarticle-template.tex
paper

We recover the scene plane via spatial resection by applying a PnP algorithm \cite{collins2014infinitesimal} to the 2D-3D correspondences obtained using a chessboard pattern. Note that this step is separate from camera calibration, yet could well be carried out using the same calibration pattern used in the camera calibration step.\footnote{The critical point is that the pattern should ideally be coplanar with the local scene plane, meaning its height above the scene plane should not exceed a few millimeters.} While a single image of such a chessboard pattern placed on the floor could be sufficient if the floor is even, we place a chessboard pattern in close proximity to the projected circles pattern in each projector calibration image in order to recover the scene plane locally to each target location, in order to account for the possibility of an uneven floor. Note that in principle, we could project a chessboard pattern instead of a circles pattern to obtain the 2D-3D correspondences needed for projector calibration; it is, however, because we rely on detecting the corners of a chessboard pattern to recover the scene plane that we opt instead for a alternative pattern.

>>>>

We recover the scene plane via spatial resection by applying a PnP algorithm \cite{collins2014infinitesimal} to the 2D-3D correspondences obtained using a chessboard pattern. Note that this step is separate from camera calibration, yet could well be carried out using the same calibration pattern used in the camera calibration step.\footnote{The critical point is that the pattern should ideally be coplanar with the local scene plane, meaning its height above the scene plane should not exceed a few millimeters.} While a single image of such a chessboard pattern placed on the floor could be sufficient if the floor is even, we place a chessboard pattern in close proximity to the projected circles pattern in each projector calibration image in order to recover the scene plane locally to each target location, in order to account for the possibility of an uneven floor (cf.\ Figure~\ref{fig:2d}(b)). Note that in principle, we could project a chessboard pattern instead of a circles pattern to obtain the 2D-3D correspondences needed for projector calibration; it is, however, because we rely on detecting the corners of a chessboard pattern to recover the scene plane that we opt instead for a alternative pattern.
